---
title: "KTool"
author: "Kate Barry"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A package giving users the capability to search for any given term and have the most valuable usernames with this term in their bios returned to them in a ranked order so that users have the ability to contact those users with similar interests to them.

## Install

Install from GitHub with the following code:

```{r install, eval = FALSE}
if (!requireNamespace("devtools", quietly = TRUE)) {
  install.packages("devtools")
}
devtools::install_github("katebarry/KTool")
```

This package uses <code>rtweet</code>. As a 
result, each user must have previously acquired authentication from Twitter and 
instructions to do that [can be found here](http://rtweet.info/articles/auth.html).

## Usage

ktool's first argument takes any Twitter query, complete with boolean operators if desired, surrounded by quotation marks.

```{r}
user_data = rtweet::search_users("term")
```

```{r usage, eval = FALSE}
## Create Twitter object of people with term in their bio
user_data = rtweet::search_users("ceo")
```

This process is only used to gather information for the user. It is then up to the user to take the usernames of those gathered by <code>ktool</code> and input them into their own Twitter account to create a base of contact between the users.
